---
title: "Building my app"
author: "Scott Brenstuhl"
date: "January 13, 2016"
output: html_document
---
```{r}
library(geosphere)
```
First I played with k-clustering with the idea that I could check the roadtrip to all those within the cluster of the user and change the cluster number up and down to find a fit. I quickly realzized that points getting pulled to other clusters makes this approach not super reliable.
```{r}
clust <- kmeans(data.frame(parks_data$lat, parks_data$long),5)

plotcluster(data.frame(parks_data$lat, parks_data$long), clust$cluster)
    
ggplot(parks_data, aes(lat, long)) +
    geom_point()

leaflet(data = parks_data) %>%
    addTiles() %>%
    addMarkers(~long, ~lat, popup = ~Name)

my_lat <- 38.00
my_long <- -122.00

c("Me", NULL, NULL, NULL, NULL, NULL, my_lat, my_long)
```

First I want to try to build my own function to do this before looking for an existing package (because it seems more fun).
Does this leave room for the fist closests first closest to be closer to home?
```{r}

var <-cbind(parks_data,dist = distHaversine(c(my_long,my_lat), as.matrix(parks_data[c('long','lat')])))
sum(var$dist)

matrix(parks_data$long, parks_data$lat)

# Find the closest two parks to a point
# begin and parks should be long, lat
closest_two <- function(begin, parks){
    distance = distHaversine(begin, parks)
    park_df = cbind(parks_data[c('Name','lat','long')], distance)
    closest = min(distance)
    n = length(distance)
    second = sort(distance, decreasing = TRUE)[n-1]
    park_df[park_df$distance == closest | park_df$distance==second,]
}

var <- NULL

for (park in parks_data$Name){
    start = subset(parks_data, Name == park)[c('long','lat')]
    distances = distHaversine(start, parks_data[c('long','lat')])
    #print(c(park, c(distances)))
    var <- rbind(var, c(park,distances))
}
var <- data.frame(var)
names(var) <- c("Parks",parks_data$Name)
names(var)
View(var)
# Will give distance of full trip including returning
round_trip <- function(trip){
    start = trip[,c('long','lat')][trip["Name"]=="Start"] %>%
        as.numeric()
    last_loc = tail(trip[,c('long','lat')],1) %>%
        as.numeric()
    sum(as.numeric(trip[,'distance'])) + distHaversine(last_loc, start)
}

trip_build <- function(trip, max_dist){
    trip_dist = round_trip(trip)
    if(trip_dist < max_dist){
        #add another location
        #trip_build(trip, max_dist)
    }else{
       #take away last and return trip
        10
    }
}

trip_build(plan,1000000)

round_trip(plan)


my_lat <- 37.767019
my_long <- -122.421781

usr_home <- c('Start', my_lat, my_long, 0)
plan <- closest_two(c(my_long,my_lat), as.matrix(parks_data[c('long','lat')]))
plan <- rbind(usr_home, plan)

```

```{r}
var2 <- NULL

for (park in parks_data$Name){
    start = subset(parks_data, Name == park)[c('long','lat')]
    distances = distHaversine(start, parks_data[c('long','lat')])
    var2 <- rbind(var2, distances)
}

var2 <- data.frame(var2)
colnames(var2) <- parks_data$Name
rownames(var2) <-parks_data$Name


    
trip <- names(sorted[1:10])

nn <- function(trip, start) {
    trip = trip[!trip == start]
    closest = var2[start,trip][which.min(var2[start,trip])]
    remaining = trip[!trip==names(closest)]
    list(closest= names(closest), remaining = remaining)
}

function(trip, start){ 
    parks_remain = trip
    ordered_trip = c("Acadia")
    for(x in 1:(length(trip)-2)){
        added = nn(parks_remain, ordered_trip[length(ordered_trip)])
        parks_remain = unlist(added['remaining'],use.names = FALSE)
        ordered_trip = c(ordered_trip, as.character(added['closest']))
    }
    if(parks_remain == 1){
        ordered_trip = c(ordered_trip, parks_remain)
    }else{
        print('Something wrong')
    }
}
ordered_trip[length(ordered_trip)]
#test <- nn(trip, 'Great Smoky Mountains')


```
